---
title: "lab"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(tidyverse)

```


## Python browser

```{r}
b <- py$browser("test")
b$signature
`````


```{r}







dockeR::doc_copy("tiktoksignature", from = "../tiktok_signature/api.R", to_cont = "/usr/api.R")
dockeR::doc_copy("tiktoksignature", from = "../tiktok_signature/run_api.R", to_cont = "/usr/run_api.R")

```




## Get individual tiktok


```{r}

res <- parse_curl_request()
res$r_code

```


1. Install docker. Once it is installed you can verify with `docker -v```

2. Set `docker = T` in tk_auth() and run the following test:

```{r}

tk_init()
if(stringr::str_length(get_docker_signature("")) > 16){
  message("Signature successfull, your docker container is working.")
} else {
  message("Unable to get the signature")
}

```

4. Verify that everything is running correctly. The output should be a character vector of three elements.

## Docker Signature


```{r}

system("docker run -dt --rm --name tiktoksignature tiktoksignature:latest ")

res <- system("docker exec -t tiktoksignature /bin/python3 /usr/app/sign.py 'aa'", intern = T)
jsonlite::fromJSON(res)


system("docker start tiktapi")
# system("docker run -d -p 8080:8080 -v $(pwd):/usr/app --name tiktapi tiktapi")



system("docker run -d -p 8080:8080 -v $(pwd):/usr/app --name tiktapi tiktapi")


docker build . -t tiktokapi:latest
docker run -v TikTokApi --rm tiktokapi:latest python3 your_script.py


port <- 32770

res <- httr::POST(
  url = glue::glue("http://localhost:{port}"), 
  body = "dd", timeout = httr::timeout(2))

rawToChar(res$content)

jsonlite::fromJSON(rawToChar(res$content))$signature


```


```{r}
query <- "mysterious_by_nature"

shape_url <- function(){
  
  # base_url <- "https://m.tiktok.com/api/item_list/?aid=1988"
  base_url <- "https://www.tiktok.com/node/share/user/@mysterious_by_nature?aid=1988"
  
  
  # url_params$app_name <- "tiktok_web"     
  # url_params$device_platform <- "web"     
  # url_params$referer <- ""  
  # url_params$root_referer <- ""           
  # url_params$cookie_enabled <- "true"  
  # url_params$screen_width <- "1440"       
  # url_params$screen_height <- "900"       
  # url_params$browser_language <- "fr-FR"  
  # url_params$browser_platform <- "MacIntel" 
  # url_params$browser_online <- "true"                                                                                                 
  # url_params$ac <- "4g"             
  # url_params$timezone_name <- "America%2FToronto"                                                                                                       
  # url_params$priority_region <- ""  
  # url_params$appId <- "1233"                                                         
  # url_params$region <- "CA"                                                          
  #url_params$appType <- "m"                                                          
  #url_params$isAndroid <- "true"                                                    
  #url_params$isMobile <- "false"                                                     
  #url_params$isIOS <- "false"                                                        
  #url_params$OS <- "mac"     
  # url_params$language <- "fr" 
  # url_params$did <- "6893606546577982982"   
  # url_params$browser_name <- str_extract(ua, ".*?(?=\\/)")
  # url_params$browser_version <- encode_string(str_remove(ua, ".*?\\/"))
  # url_params$page_referer <- encode_string("https://www.tiktok.com/foryou")   
  
  ## User Query
  # url_params$uniqueId <- "mysterious_by_nature"
  # url_params$secUid <- "MS4wLjABAAAAzoTMYqYafiGwnL-hR8DflXL6CSuvU5wDLmz5NdxchWbbR0XL7XuYWq-4XRb4_ldr"
  # url_params$validUniqueId <- "mysterious_by_nature"
  
  url_params <- list()  
  url_params$id <- "6727327145951183878"
  url_params$secUid <- "MS4wLjABAAAA8ezUaW4ecJX222ObGXxt07F9BIh4QH3-g1P1DHyChT2LLi2cn-vAE2R53-H672ZO"
  
  
  url_params$count <- "50"
  url_params$maxCursor <- "1604716686000"
  url_params$minCursor <- "0"
  url_params$sourceType <- "8"
  
  ua <- "Mozilla/5.0 (Macintosh; Intel Mac OS X 10_14_7) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/86.0.4240.198 Safari/537.36"
  url_params$user_agent <- encode_string(ua)
  url_params$verifyFp <- paste0("verify_", get_verify())
  
  
  query <- url_params %>% imap_chr(~paste0("&", .y, "=", .x)) %>% paste(collapse = "")  %>% paste0(base_url, .)
  final_url <- get_signature(url, ua = ua, port = NULL)
  tiktok_res <- httr::GET(final_url, httr::add_headers(.headers = c("user-agent" = ua)))
  jsonlite::fromJSON(rawToChar(tiktok_res$content))
  
  user_posts <- tk_posts(scope = "user", query = "willsmith", n = 50)
  
  
}

````





