---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tiktokr

<!-- badges: start -->
<!-- badges: end -->

The goal of `tiktokr` is to provide a scraper for the video-sharing social networking service [TikTok](http://tiktok.com/). Mostly inspired by this Python module: [davidteather/TikTok-Api](https://github.com/davidteather/TikTok-Api). You will need Python 3.6 or higher to use `tiktokr`.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r eval = F}
# install.packages("devtools")
devtools::install_github("benjaminguinaudeau/tiktokr")
```

Load library

```{r example}
library(tiktokr)
## basic example code
```

## Example

This is a basic example which shows you how to solve a common problem:

Make sure to use your preferred Python installation

```{r}
library(reticulate)

use_python(py_config()$python)

```

Initialize `tiktokr`

```{r}
init_tiktokr()

```

### Get TikTok trends

Returns a tibble with trends.


```{r, eval = F}
# Trend
trends <- get_trending(200)



```

### Get TikToks from user name

```{r, eval = F}
# Username
user <- get_username("willsmith")
user_posts <- get_user_post(200, "willsmith")

```

### Get TikToks from hashtag

```{r, eval = F}
hash <- get_hashtag("maincharacter")
hash_post <- get_hashtag_post(100, "maincharacter")

discover_hashtags(100)

```

### Download TikTok Videos

From Trends:

```{r, eval = F}
trends <- get_trending(200)

trends %>%
  split(1:nrow(.)) %>% 
  purrr::walk(~{download_video(.x$downloadAddr, paste0("video/", .x$id, ".mp4"))})

```

From hashtag:

```{r, eval = F}

hash <- get_hashtag_post(20, "trump2020")


trends %>%
  head(20) 

hash %>%
  split(1:nrow(.)) %>% 
  purrr::walk(~{download_video(.x$downloadAddr, paste0("video/hashtag/", .x$id, ".mp4"))})

```


